Pattern Avoidance

### 2014-11-07 project2/paper/paper.tex
changed theorem numbering
capitalization
attributions
missing comma
typo in section 1

\newtheoremstyle{theorem}{1em}{1em}{\slshape}{0pt}{\bfseries}{.}{ }{}
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{claim*}{Claim}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem*{remark*}{Remark}
\newtheorem{algorithm}{Algorithm}
\newtheorem*{question*}{Question}
\newtheorem{question}{Question}
\newtheorem{example}{Example}

@@

@@

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{R}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the reversing lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{F}(\pi)$. 
\end{proof}

@@

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{F}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the flipping lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{F}(\pi)$. 
\end{proof}
\section{Avoiding Permutations of Length Three Part I}
\label{312}

@@

@@

@@

In this section we present our findings and conjectures about sequences $s_n(\pi)$ for $\pi\in S_4$. Using the flipping and reversing operators we can group elements of $S_4$ by their orbits. The following groups appear: 
$$
\{1234,4321\},
\{1243,4312,2134,3412\},
\{1432,4123,2341,3214\},
\{2143,3412\},
$$
$$
\{4132,1423,2314,3241\},
\{4213,1342,3124,2431\},
\{2413,3142\}
$$
$$
\{4231,1324\}
$$
So all permutations that belong to a single group in the list above must produce the same sequence. 
We computed values up to $s_{9}$. It appears that there are three sequences that appear, and we have sorted the permutations according to which sequence they produce and paired them with their flips.

@@

\section{Avoidance of permutations of $T_n$}
\label{Tn}
We now impose further restrictions on the set of permutations $S_n$. This new set of permutations, $T_n$ is defined as follows.

@@

>>>>

\newtheoremstyle{theorem}{1em}{1em}{\slshape}{0pt}{\bfseries}{.}{ }{}
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{claim*}{Claim}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{remark*}{Remark}
\newtheorem{algorithm}{Algorithm}
\newtheorem*{question*}{Question}
\newtheorem{question}{Question}
\newtheorem{example}[theorem]{Example}

@@

\emph{Yajit wrote this section. }

@@

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{R}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the reversing lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{R}(\pi)$. 
\end{proof}

@@

\begin{corollary} 
For a permutation $\pi$, $s_n(\pi)=s_n(\mathcal{F}(\pi))$. 
\end{corollary}
\begin{proof}
This result follows because the flipping lemma gives a bijection between permutations that avoid $\pi$ and permutations that avoid $\mathcal{F}(\pi)$. 
\end{proof}

\emph{Yajit wrote this section.}

\section{Avoiding Permutations of Length Three Part I}
\label{312}

@@

\emph{Deepak wrote this section.}

@@

\emph{Leon wrote this section. Yajit edited this section.}

@@

In this section we present our findings and conjectures about sequences $s_n(\pi)$ for $\pi\in S_4$. Using the flipping and reversing operators we can group elements of $S_4$ by their orbits. The following groups appear: 
$$
\{1234,4321\},
\{1243,4312,2134,3412\},
\{1432,4123,2341,3214\},
\{2143,3412\},
$$
$$
\{4132,1423,2314,3241\},
\{4213,1342,3124,2431\},
\{2413,3142\},
$$
$$
\{4231,1324\}
$$
So all permutations that belong to a single group in the list above must produce the same sequence. 
We computed values up to $s_{9}$. It appears that there are three sequences that appear, and we have sorted the permutations according to which sequence they produce and paired them with their flips.

@@

\

\emph{Yajit wrote this section.}

\section{Avoidance of Permutations of $T_n$}
\label{Tn}
We now impose further restrictions on the set of permutations $S_n$. This new set of permutations, $T_n$ is defined as follows.

@@

\

\emph{Deepak wrote this section. Leon and Yajit closely edited this section.}
